--- 
title: "Genomics with R for biologists"
author: "Ines Lucia Patop: inespatop@brandeis.edu"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is the index for the coursebook"

---
```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(DESeq2) #for differential expression analysis
library(ggplot2) #for 2D graph
library(ggrepel) #to get the names in ggplot graph 
library(gridExtra)
library(factoextra)
library(plotly) #for 3D graphics
library(plyr)#table manipulation
library(dplyr)#table manipulation
library(tidyr)#table manipulation
library("RColorBrewer")
library("pheatmap")
library(org.Dm.eg.db)#get annotation
library(MetaCycle) # to identify cycling genes, the successor of JTK according to JTK authors
library(pcaExplorer)
library(GenomicFeatures) #This is an R package to deal with genomic data. You can read more at https://bioconductor.org/packages/release/bioc/vignettes/GenomicFeatures/inst/doc/GenomicFeatures.pdf
library(ChIPpeakAnno) 
library(ChIPseeker)#This is a package to annotate Chip-Peaks data https://bioconductor.org/packages/release/bioc/vignettes/ChIPpeakAnno/inst/doc/ChIPpeakAnno.html
```

```{r cite-packages, include = FALSE}
# automatically create a bib database for R packages
# add any packages you want to cite here
knitr::write_bib(c(
  .packages(), 'bookdown', 'tidyverse'
), 'packages.bib')

```

# Overview {-}

The idea of the practical part will be to give you tools to be able to manage regular data-analysis in molecular biology labs. Also we think that this training in basic programing and statistics will be of high value for your future projects.

## Course Aims

* Learn basic coding intuition and usage of R for analysis and plots.
* Undestand the main issues we have to deal with in Genomics.
* Learn how to do basic analysis, Chipseq, RNAseq, SingleCell.

## Intended Learning Outcomes

By the end of this course students will be able to:

* Create your own R code.
* Do basic and complex analysis.
* Read and understand R code.

## Next steps

I have a project on shell commands for biologist. Will be available soon.

## Data availability

All the data used in this book is publiclily available. Preprocessed files can be found in this [reposotory](https://drive.google.com/drive/folders/1OcgvixGUpd3N2sU4ysnq1B-wOmi6uO27?usp=sharing)

## Acknowledgments

Ane Martin Anduaga and Sebastian Kadener for usefull discussion.



